The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-08-01 paper.tex
fix some plots

\renewcommand{\b}{\pmb}
\renewcommand{\d}{{\rm d}}
\newcommand{\atikh}{\b{\hat a}_\text{Tikhonov}}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

@@

@@

\begin{figure*}[p]
    \includegraphics[width=\textwidth]{figures/flux-scale/flux-scale}
    \caption{
        This figure shows the measured fluxes (black points) of 11 sources plotted against the
        published spectra from \citet{2017ApJS..230....7P} (solid line above 50 MHz, dotted line
        below 50 MHz), \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B}
        (dot-dash line).
    }
    \label{fig:flux-scale}
\end{figure*}

@@

\begin{deluxetable*}{CCCCCC}
    \tablecaption{Summary of the generated all-sky maps\label{tab:summary}}
    \tablewidth{0pt}
    \tablehead{
        \colhead{} & \colhead{Frequency} & \colhead{Bandwidth} & \colhead{FWHM} &
            \colhead{Noise} & \colhead{Noise} \\
        \colhead{\#} & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{(arcmin)} &
            \colhead{(K)} & \colhead{(Jy)}
    }
    \startdata
    1 & 36.528 & 0.024 & 16.2 & 372.8 \\
    2 & 41.760 & 0.024 & 14.7 & 321.2 \\
    3 & 46.992 & 0.024 & 14.2 & 247.0 \\
    4 & 52.224 & 0.024 & 13.6 & 205.7 \\
    5 & 57.456 & 0.024 & 13.5 & 167.7 \\
    6 & 62.688 & 0.024 & 13.5 & 137.6 \\
    7 & 67.920 & 0.024 & 13.5 & 114.9 \\
    8 & 73.152 & 0.024 & 13.7 &  93.4 \\
    \enddata
\end{deluxetable*}

\begin{figure*}[ht]
    \plotone{maps/2017-04-20-rgb-map-smaller}
    \caption{
        This Mollweide-projected map is constructed from 3 maps of the sky at 41.760 MHz (red),
        57.456 MHz (green), and 73.152 MHz (blue) using data from the Owens Valley Long Wavelength
        Array. These maps were constructed using $m$-mode analysis imaging. 8 bright radio sources
        have been subtracted from the sky (Cyg A, Cas A, Vir A, Tau A, Hya A, Her A, Per B, and 3C
        353). The hole corresponds to declinations less than $-30^\circ$. Most of the diffuse
        emission is synchrotron, but the blue regions mottling the galactic plane are due to
        free-free absorption from \ion{H}{2} regions.
    }
    \label{fig:rgb}
\end{figure*}

\begin{figure*}[p]
    \gridline{
        \fig{figures/channel-maps/spw04-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw06-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/channel-maps/spw08-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw10-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/channel-maps/spw12-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw14-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/channel-maps/spw16-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
        \fig{figures/channel-maps/spw18-glamour-shot-map-wiener-filtered-rainy-2048-galactic.pdf}
            {0.48\textwidth}{}
    }
    \caption{
        Mollweide-projected maps of the VHF sky north of $-30^\circ$ generated using the OVRO-LWA
        and $m$-mode analysis imaging. The properties of each map are summarized in
        Table~\ref{tab:summary}. The color scale is logarithmic and has units of Kelvin. As
        described in the text, 8 bright sources have been subtracted. The small blank region near
        the bottom of each map corresponds to the region of sky within 2 degrees of the Sun at the
        time of the observations.
    }
    \label{fig:channel-maps}
\end{figure*}

>>>>

\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

\renewcommand{\b}{\pmb}
\newcommand{\tbf}{\textbf}
\renewcommand{\d}{{\rm d}}
\newcommand{\atikh}{\b{\hat a}_\text{Tikhonov}}

@@

\watermark{draft}

@@

\begin{figure*}[ht]
    \includegraphics[width=\textwidth]{figures/flux-scale/flux-scale}
    \caption{
        This figure shows the measured fluxes (black points) of 11 sources plotted against the
        published spectra from \citet{2017ApJS..230....7P} (solid line above 50 MHz, dotted line
        below 50 MHz), \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B}
        (dot-dash line).
    }
    \label{fig:flux-scale}
\end{figure*}

@@

\begin{table*}[ht]
    \centering
    \begin{tabular}{cccccc}
        \hline
        \hline
        & \tbf{Frequency} & \tbf{Bandwidth} & \tbf{FWHM} & \multicolumn2c{\tbf{Thermal Noise}} \\
        \cline{5-6}
        \tbf{\#} & (MHz)  & (MHz)          & (arcmin)  & (K) & (Jy) \\
        \hline
        1 & 36.528 & 0.024 & 16.2 & 372.8 & \\
        2 & 41.760 & 0.024 & 14.7 & 321.2 & \\
        3 & 46.992 & 0.024 & 14.2 & 247.0 & \\
        4 & 52.224 & 0.024 & 13.6 & 205.7 & \\
        5 & 57.456 & 0.024 & 13.5 & 167.7 & \\
        6 & 62.688 & 0.024 & 13.5 & 137.6 & \\
        7 & 67.920 & 0.024 & 13.5 & 114.9 & \\
        8 & 73.152 & 0.024 & 13.7 &  93.4 & \\
        \hline \hline
    \end{tabular}
    \caption{Summary of the generated all-sky maps\label{tab:summary}}
\end{table*}

%\begin{figure*}[p]
%    \centering
%    \includegraphics[width=0.9\textheight, angle=90]{maps/2017-04-20-rgb-map-smaller}
%    \caption{
%        This Mollweide-projected map is constructed from 3 maps of the sky at 41.760 MHz (red),
%        57.456 MHz (green), and 73.152 MHz (blue) using data from the Owens Valley Long Wavelength
%        Array. These maps were constructed using $m$-mode analysis imaging. 8 bright radio sources
%        have been subtracted from the sky (Cyg A, Cas A, Vir A, Tau A, Hya A, Her A, Per B, and 3C
%        353). The hole corresponds to declinations less than $-30^\circ$. Most of the diffuse
%        emission is synchrotron, but the blue regions mottling the galactic plane are due to
%        free-free absorption from \ion{H}{2} regions.
%    }
%    \label{fig:rgb}
%\end{figure*}

\begin{figure*}[ht]
    \includegraphics[width=\textwidth]{figures/channel-maps/channel-maps}
    \caption{
        Mollweide-projected maps of the VHF sky north of $-30^\circ$ generated using the OVRO-LWA
        and $m$-mode analysis imaging. The properties of each map are summarized in
        Table~\ref{tab:summary}. The color scale is logarithmic and has units of Kelvin. As
        described in the text, 8 bright sources have been subtracted. The small blank region near
        the bottom of each map corresponds to the region of sky within 2 degrees of the Sun at the
        time of the observations.
    }
    \label{fig:channel-maps}
\end{figure*}
